\huge A Usability Evaluation of Tor Launcher

### 2016-11-11 pets2017-paper/pets2017-paper.tex

\subsection{Recruitment}
We recruited people from Craigslist using the recruitment text in Appendix~\ref{qualitative-recruitment}, which linked an prescreening survey that collected demographics (Appendix~\ref{qualitative-prescreening}). We pre-screened~\cite{screening} for diversity in gender, age, technical expertise, use of security tools, and familiarity with Tor in a small participant pool. {\color {red} Of our 16 recruited participants, 53.3\% were male. Ages ranged from 20 to~62 years ($\mu = 24.5$, $\sigma = 12.6$). 93.3\% of our participants had college education.} We took participants' self-reported familiarity with technical terms use of security tools with skepticism (Appendix~\ref{prescreening-responses}). We verified their self-reported familiarity with Tor Browser in-person, and found that 4 used it, 5 heard of it but not used it, and the remaining 8 never heard of or used it. The main objective of this question was to identify new users versus infrequent users. We considered participants who had never heard of Tor or have only heard of Tor to be new users and those who have used Tor to be previous users.

@@

%success rate and version
Our interface changes did {\it not} have a significant impact on completion rates (Pearson's Chi-squared; $X^2 = 0.0126$, $df = 2$, $p = 0.994$). That is, the slight differences in completion rates between E1-NEW vs E1-OLD, E2-NEW vs E2-OLD and E3-NEW vs E3-OLD are likely due to random chance.

@@

\begin{table}[h]
\centering
\begin{tabular}{l r r}
& Familiarity\\
\noalign{\hrule}
Malware & 00/00\\
Proxy services & 00/00\\
Phishing & 00/00\\
SSL & 00/00\\
X.511 certificates & 00/00\\
Tor & 00/00\\
\end{tabular}
\caption{
An overview of the results of the experiment. Those who
failed to connect were assigned the maximum time of 40:08.
}
\label{table:selfreported-tech}
\end{table}

>>>>

\subsection{Recruitment}
We recruited people from Craigslist using the recruitment text in Appendix~\ref{qualitative-recruitment}, which linked an prescreening survey that collected demographics (Appendix~\ref{qualitative-prescreening}). We pre-screened~\cite{screening} for diversity in gender, age, technical expertise, use of security tools, and familiarity with Tor in a small participant pool. Of our 16 recruited participants, 50\% were male. Ages ranged from 20 to~62 years ($\mu = 30.5$, $\sigma = 13.5$). One participant declined to submit their age, so the previous calcuations were done without thier information. 100\% had at least some college education. We took participants' self-reported familiarity with technical terms use of security tools with skepticism (Appendix~\ref{prescreening-responses}). We verified their self-reported familiarity with Tor Browser in-person, and found that 4 used it, 5 heard of it but not used it, and the remaining 8 never heard of or used it. The main objective of this question was to identify new users versus infrequent users. We considered participants who had never heard of Tor or have only heard of Tor to be new users and those who have used Tor to be previous users.

% gender: Male: 8/Female: 8
% education: At least some college 16
% ages: 22, 23, 34, 52, 25, 22, 29, 21, 25, didn't answer, 20, 20, 26, 24, 62, 52

@@

%success rate and version
Our interface changes did {\it not} have a significant impact on completion rates (Pearson's Chi-squared; $\chi^2 = 0.0126$, $df = 2$, $p = 0.994$). That is, the slight differences in completion rates between E1-NEW vs E1-OLD, E2-NEW vs E2-OLD and E3-NEW vs E3-OLD are likely due to random chance.

@@

\begin{table}[h]
\centering
\begin{tabular}{l r r}
& Familiarity\\
\noalign{\hrule}
Malware & 81\% (13/16) \\ %13/16
Proxy services & 69\% (11/16)\\ %11/16
Phishing & 63\% (10/16)\\ %10/16
SSL & 63\% (10/16)\\%10/16
X.511 certificates & 25\% (4/16)\\ %4/16
Tor & 50\% (8/16)\\ %8/16
\end{tabular}
\caption{
An overview of the results of the experiment. Those who
failed to connect were assigned the maximum time of 40:08.
}
\label{table:selfreported-tech}
\end{table}
